\documentclass{res} 
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{colorlinks,urlcolor=black}
\newsectionwidth{10pt}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newcommand{\tab}[1]{\hspace{.2\textwidth}\rlap{#1}}
%\documentcliass[11pt]{article} %Sets the default text size to 11pt and class to article.
%------------------------
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 
\linespread{1.15} %This controls line spacing throughout the whole document 
\begin{document}
\raggedright
\centerline{\LARGE \textbf{Doris Jung-Lin Lee}} 
\vspace{-10pt}
\noindent %Prevents the following text from being indented
\centerline{ \href{mailto:dorisjunglinlee@gmail.com}{dorisjunglinlee@gmail.com} $\bullet$
\href{http://dorisjunglinlee.com}{dorisjunglinlee.com}$\bullet$
 GitHub: \href{https://github.com/dorisjlee}{dorisjlee} }
\vspace{1pt}
 \vspace{5pt}
\begin{resume}
\vspace{-30pt}
\section{EDUCATION}
\vspace{5pt}  
    \itab{Ph.D. Computer Science, University of Illinois, Urbana-Champaign} \tab{} \tab{} \tab{\quad\quad\quad\quad\quad\quad\quad\quad\quad Aug 2016 - Present} \\
\vspace{5pt}  
    \itab{B.A. Physics, Astrophysics, University of California, Berkeley} \tab{} \tab{} \tab{\quad\quad\quad\quad\quad\quad\quad\quad Sept 2013 - May 2016}

\vspace{-2pt}
\section{RESEARCH EXPERIENCE}
\vspace{-5pt}
     \begin{tabbing}
     \hspace{2.3in}\= \hspace{2.6in}\= \kill 
    {Research Intern at Tableau Software}  \>\hspace{230pt}  Summer 2018 \\
   \hspace{2.3in}\= \hspace{2.6in}\= \kill 
    {Graduate Student Research Assistant at UIUC}  \>\hspace{205pt}  Aug 2016 - Present \\
    {Lawrence Berkeley National Lab Scientific Data Management Group}  \>\hspace{230pt}  Summer 2016 \\
    {UC Berkeley AMP Lab Big Data Genomics Group}  \>\hspace{180 pt}  January 2016 - Aug 2016 \\
    {UC Berkeley Hybrid Ecologies Lab} \>\hspace{193pt}  June 2014 - Aug 2016\\
    {Princeton Astrophysical Fluid Dynamics Group}  \>\> \hspace{43pt} Summer 2015 \\
    {UC Berkeley Star Formation Theory Group}  \>\hspace{171pt}  November 2014 - Aug 2016 \\
    {University of Illinois Laboratory for Cosmological Data Mining}  \> \>\hspace{10pt} May 2014 - Jan 2016 
   \end{tabbing}    
\vspace{-20pt}
\section{PUBLICATIONS}
\vspace{-5pt}
\section{Full Papers}
\begin{itemize}
\item \textbf{Doris Jung-Lin Lee}, Aditya Parameswaran, \href{}{``The Case for a Visual Discovery Assistant: A Holistic Solution for Accelerating Visual Data Exploration}. \textit{IEEE Data Engineering Bulletin''}, September 2018.
\item \textbf{Doris Jung-Lin Lee}, John Lee, Tarique Siddiqui, Jaewoo Kim, Karrie Karahalios, Aditya Parameswaran, ``Accelerating Scientific Data Exploration via Visual Query Systems'' (2017). [\href{https://arxiv.org/abs/1710.00763}{arXiv:1710.00763}].  
\item \href{http://aaai.org/ocs/index.php/HCOMP/HCOMP16/paper/viewFile/14027/13638}{\textbf{Doris Jung-Lin Lee}, Joanne Lo, Moonhyok Kim, Eric Paulos, Crowdclass: Designing classification-based citizen science learning modules. \textit{The Fourth AAAI Conference on Human Computation and Crowdsourcing (HCOMP)}, Austin, Texas, November 2016.}
\item \href{http://dl.acm.org/citation.cfm?id=2901885&CFID=765226474&CFTOKEN=46922780}{Joanne Lo, \textbf{Doris Jung-Lin Lee}, Nathan Wong, David Bui, Eric Paulos,``Skintillates: Towards Epidermal Interactions".  \textit{ACM Designing Interactive Systems (DIS)}, Brisbane, Australia, June 2016. \textbf{Honorable Mention.}}
\item \href{http://dl.acm.org/citation.cfm?id=2858192&CFID=765226474&CFTOKEN=46922780}{Laura Devendorf, Joanne Lo, Noura Howell, \textbf{Doris Jung-Lin Lee}, Nan-Wei Gong, M. Emre Karagozler, Ivan  Poupyrev, Eric Paulos, Kimiko Ryokai,``\hspace{1pt}`I don't want to wear a screen': Probing perceptions of and  possibilities for dynamic displays on clothing''. \textit{ACM Transactions on Computer-Human Interaction (CHI)}, San Jose, USA, May 2016. \textbf{Best Paper Award.}}
\end{itemize}
\vspace{-10pt}
\section{Workshop/Short Papers}
\begin{itemize}
\item \textbf{Doris Jung-Lin Lee}, Akash Das Sarma, Aditya Parameswaran, \href{http://ceur-ws.org/Vol-2173/paper10.pdf}{``Aggregating Crowdsourced Image Segmentations''}. \textit{The Sixth AAAI Conference on Human Computation and Crowdsourcing (HCOMP)}, Zurich, Switzerland, July 2018.
\item Edward W Huang, Sheng Wang, \textbf{Doris Jung-Lin Lee}, Runshun Zhang, Baoyan Liu, Xuezhong Zhou, ChengXiang Zhai. \href{https://amia2017.zerista.com/event/member/389402}{``Framing Electronic Medical Records as Polylingual Documents in Query Expansion''}\textit{AMIA Annual Symposium Proceedings}. American Medical Informatics Association, 2017.
\item \textbf{Doris Jung-Lin Lee}, Jinda Han, Dana Chambourova, Ranjitha Kumar. \href{https://kddfashion2017.mybluemix.net/final_submissions/ML4Fashion_paper_21.pdf}{``Identifying Fashion Accounts in Social Networks''}.  \textit{In Proceedings of ACM KDD 2017 Machine learning meets fashion Workshop}, Halifax, Nova Scotia, August 2017.
\item Ling Jin, \textbf{Doris Jung-Lin Lee}, Alex Sim, Sam Borgeson, John Wu, Anna Spurlock, Annika Todd, \href{https://sdm.lbl.gov/perf/AISGSB2017-final2.pdf}{``Comparison of Clustering Techniques for Residential Energy Behavior using Smart Meter Data''}, \textit{2nd International Workshop on Artificial Intelligence for Smart Grids and Smart Buildings} In conjunction with AAAI 2017.
\item \textbf{Doris Jung-Lin Lee}, Robert J. Brunner, ``Pattern Discovery and Large-Scale Data Mining on Cosmological Datasets". \textit{6th Workshop on Algorithms for Modern Massive Data Set (MMDS)}, Berkeley, USA, June 2016.  [\href{http://dorisjunglinlee.com/files/MMDS_poster.pdf}{Poster}]
\end{itemize}
\vspace{-10pt}
\section{Technical Reports}
\begin{itemize}
\item \textbf{Doris Jung-Lin Lee}, Aaron T. Lee, ``astroSim: Jupyter Notebook tutorials for running astrophysical simulations through the gravitational collapse of a magnetized, rotating sphere``. Zenodo. [\href{http://doi.org/10.5281/zenodo.59657}{zenodo:59657}]
\item \textbf{Doris Jung-Lin Lee}, Robert J. Brunner, ``Creating updated, scientifically-calibrated mosaic images for the RC3 Catalogue"(2015) [\href{http://arxiv.org/abs/1512.01204}{arXiv:1512.01204}]. 
\end{itemize}
\section{PRESENTATIONS}
\begin{itemize}
\item Crowdclass: Designing classification-based citizen science learning modules. [\href{http://dorisjunglinlee.com/files/crowdclass_slides.pdf}{Slides}]
	\begin{itemize}[label={$\circ$}]
	\item 10/31/16 HCOMP, Austin, Texas
	\item 10/18/16 UIUC HCI Seminar, Champaign, Illinois
	\item 10/13/16 Zooniverse Seminar at Adler Planetarium, Chicago, Illinois
	\end{itemize}
%\item 06/23/16 \textbf{Doris Jung-Lin Lee}, Robert Brunner, ``Pattern Discovery and Large-Scale Data Mining on Cosmological Datasets".  6th Workshop on Algorithms for Modern Massive Data Set (MMDS).  [\href{http://dorisjunglinlee.com/files/MMDS_poster.pdf}{Poster}]
\item 05/05/16 Alyssa Morrow, Eric Tu, Frank Austin Nothaft, George He, \textbf{Doris Lee},  Anthony Joseph, David Patterson. ``Mango: data exploration on large genomic datasets". UC Berkeley College of Engineering Undergraduate Research Symposium.
\item 08/08/15 \textbf{Doris Lee}, Kengo Tomida, James Stone, ``Three-Dimensional Simulations of Instabilities in Accretion Disk Torus". Princeton University Undergraduate Summer Research Program Final Presentation. [\href{http://dorisjunglinlee.com/files/PrincetonUSRPreport.pdf}{Technical Report}]
\item 03/25/15 \textbf{Doris Lee}, Robert Brunner,``Creating updated, scientifically-calibrated mosaic images for the RC3 Catalogue". Society of Physics Students West Coast Zone Meeting. [\href{http://dorisjunglinlee.com/files/rc3_poster_sps_zone_meeting.pdf}{Poster}]
\end{itemize}
\section{PATENTS}
\begin{itemize}
\item \textit{Skintillates: Towards Epidermal Electronics Interactions.} Eric Paulos, Joanne Lo, Jung-Lin Lee, U.S. Provisional Patent Application No.62/174,735, June 2015.
\item \textit{Individually Addressable, Highly Efficient, Trifunctional Conductive Thread.} Eric Paulos, Kimiko Ryokai, Joanne Lo, Laura Devendorf, Jung-Lin Lee, Nan-Wei Gong, Karen Robinson, Ivan Poupyrev, June 2015.
\end{itemize}
\section{AWARDS}
\begin{itemize}
\item UIUC Computer Science Excellence Fellowship \hspace{80pt}\tab{Oct 2016}
\item ACM DIS 2016 Honorable Mention Award \hspace{95pt}\tab{June 2016}
\item ACM CHI 2016 Best Paper Award\hspace{133pt}\tab{May 2016}
%\item UC Berkeley Student Opportunity Fund Travel Award \hspace{15pt}\tab{March 2016}
\end{itemize}
\section{SERVICE} 
\itab{} \itab{Mentoring:}
\\ \itab{} \quad Moonhyook Kim (UC Berkeley, 2016), Akari Asai (UC Berkeley, 2016), Dana Chambourova\quad (UIUC Senior Thesis, 2017), Jaewoo Kim (UIUC, 2017), Yanqing Ma (UIUC, 2017), Huizi Hu(UIUC, 2017)
\\ \itab{} \itab{ACM TIIS 2018 Reviewer}\hspace{279pt}
\\ \itab{} \itab{ACM IUI 2018 Program Committee}\hspace{279pt}
\\ \itab{} \itab{ACM CHI 2018 Reviewer}\hspace{279pt}
\\ \itab{} \itab{ACM SIGCHI Executive Committee 2017 Student Volunteer}\hspace{279pt}
\\ \itab{} \itab{ACM IUI 2017 Reviewer}\hspace{279pt}
\\ \itab{} \itab{ACM XRDS Magazine News Editor}\hspace{255pt}\tab{Nov 2014-August 2016}
\\ \itab{} \itab{Organization Mentor for Google Code-In youth programming contest}\hspace{279pt}\tab{2015-2016 Season}
% \\ \itab{} \itab{Peer Mentor and Club Liaison for Society of Physics Students}\hspace{266pt}\tab{Sept 2015-May 2016}
% \\ \itab{} \itab{Volunteer and Summer Program Coordinator at Berkeley COMPASS Project}\hspace{267pt}\tab{Sept 2013-May 2016}
\end{resume}
\end{document}