\documentclass{res} 
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{colorlinks,urlcolor=black}
\newsectionwidth{10pt}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newcommand{\tab}[1]{\hspace{.2\textwidth}\rlap{#1}}
\newcommand{\rfill}{\hspace*{\fill}}
\newcommand{\studentinfo}[1]{\textit{\textcolor{gray}{(#1)}}}
\newenvironment{denselist}{
    \begin{list}{\small{$\bullet$}}%
    {\setlength{\itemsep}{0ex} \setlength{\topsep}{0ex}
    \setlength{\parsep}{0pt} \setlength{\itemindent}{0pt}
    \setlength{\leftmargin}{1.5em}
    \setlength{\partopsep}{0pt}}}%
    {\end{list}}

\newcommand{\squishlist}{
   \begin{list}{$\bullet$}
    { \setlength{\itemsep}{0pt}
      \setlength{\parsep}{2pt}
      \setlength{\topsep}{0pt}
      \setlength{\partopsep}{0pt}
      \leftmargin=25pt
\rightmargin=0pt
\labelsep=5pt
\labelwidth=10pt
\itemindent=0pt
\listparindent=0pt
\itemsep=\parsep
    }
}

%\documentcliass[11pt]{article} %Sets the default text size to 11pt and class to article.
%------------------------
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 
\linespread{1.15} %This controls line spacing throughout the whole document 
\begin{document}
\raggedright
\centerline{\LARGE \textbf{Doris Jung-Lin Lee}} 
\vspace{-10pt}
\noindent %Prevents the following text from being indented
\centerline{ \href{mailto:dorisjunglinlee@gmail.com}{dorisjunglinlee@gmail.com} $\bullet$
\href{http://dorisjunglinlee.com}{dorisjunglinlee.com}$\bullet$
 GitHub: \href{https://github.com/dorisjlee}{dorisjlee} }
\vspace{1pt}
 \vspace{5pt}
\begin{resume}
\vspace{-30pt}
\section{EDUCATION}
\vspace{5pt}Ph.D. Computer Science, University of Illinois, Urbana-Champaign\rfill Aug 2016 - Present
\\\vspace{5pt}B.A. Physics, Astrophysics, University of California, Berkeley \rfill Sept 2013 - May 2016
\vspace{-2pt}
\section{RESEARCH EXPERIENCE}
\vspace{2pt}
Research Intern at Tableau Software \rfill Summer 2018 \\
Graduate Student Research Assistant at UIUC \rfill Aug 2016 - Present \\ 
Lawrence Berkeley National Lab Scientific Data Management Group \rfill Summer 2016 \\
UC Berkeley AMP Lab Big Data Genomics Group \rfill January 2016 - Aug 2016 \\
UC Berkeley Hybrid Ecologies Lab \rfill  June 2014 - Aug 2016\\
Princeton Astrophysical Fluid Dynamics Group \rfill Summer 2015 \\
UC Berkeley Star Formation Theory Group \rfill November 2014 - Aug 2016 \\
University of Illinois Laboratory for Cosmological Data Mining \rfill May 2014 - Jan 2016 
\section{PUBLICATIONS}
\vspace{-5pt}
\section{Full Papers}
\begin{itemize}[leftmargin=0in,label={}]
\item \textbf{[P6]} \textbf{Doris Jung-Lin Lee}, John Lee, Tarique Siddiqui, Jaewoo Kim, Karrie Karahalios, Aditya Parameswaran. \href{https://arxiv.org/abs/1710.00763}{You can't always sketch what you want: Understanding Sensemaking in Visual Query Systems}. Under Submission to EuroVis 2019.
\item \textbf{[P5]} \textbf{Doris Jung-Lin Lee}, Himel Dev, Hazem Elmeleegy, Aditya Parameswaran. Avoiding the Drill-down Fallacy with Storyboard: Assisted and Accelerated Data Exploration Through Data Subsets. \textit{ACM Intelligent User Interface (IUI)}, Los Angelos, California, March 2019.
\item \textbf{[P4]} \textbf{Doris Jung-Lin Lee}, Aditya Parameswaran, \href{http://sites.computer.org/debull/A18sept/p3.pdf}{The Case for a Visual Discovery Assistant: A Holistic Solution for Accelerating Visual Data Exploration}. \textit{IEEE Data Engineering Bulletin}, Special Issue on Insights and Explanations in Data Analysis, September 2018.
\item \textbf{[P3]} \href{http://aaai.org/ocs/index.php/HCOMP/HCOMP16/paper/viewFile/14027/13638}{\textbf{Doris Jung-Lin Lee}, Joanne Lo, Moonhyok Kim, Eric Paulos, Crowdclass: Designing Classification-based Citizen Science Learning Modules. \textit{The Fourth AAAI Conference on Human Computation and Crowdsourcing (HCOMP)}, Austin, Texas, November 2016.}
\item \textbf{[P2]} \href{http://dl.acm.org/citation.cfm?id=2901885&CFID=765226474&CFTOKEN=46922780}{Joanne Lo, \textbf{Doris Jung-Lin Lee}, Nathan Wong, David Bui, Eric Paulos, Skintillates: Towards Epidermal Interactions.  \textit{ACM Designing Interactive Systems (DIS)}, Brisbane, Australia, June 2016. \textbf{Honorable Mention.}}
\item \textbf{[P1]} \href{http://dl.acm.org/citation.cfm?id=2858192&CFID=765226474&CFTOKEN=46922780}{Laura Devendorf, Joanne Lo, Noura Howell, \textbf{Doris Jung-Lin Lee}, Nan-Wei Gong, M. Emre Karagozler, Ivan  Poupyrev, Eric Paulos, Kimiko Ryokai,\hspace{1pt}`I don't Want to Wear a Screen': Probing Perceptions of and Possibilities for Dynamic Displays on Clothing. \textit{ACM Transactions on Computer-Human Interaction (CHI)}, San Jose, USA, May 2016. \textbf{Best Paper Award.}}
\end{itemize}
\vspace{-10pt}
\section{Workshop/Short Papers}
\begin{itemize}[leftmargin=0in,label={}]
\item \textbf{[W5]} \textbf{Doris Jung-Lin Lee}, Akash Das Sarma, Aditya Parameswaran, \href{http://ceur-ws.org/Vol-2173/paper10.pdf}{Aggregating Crowdsourced Image Segmentations}. \textit{The Sixth AAAI Conference on Human Computation and Crowdsourcing (HCOMP)}, Zurich, Switzerland, July 2018.
\item \textbf{[W4]} Edward W Huang, Sheng Wang, \textbf{Doris Jung-Lin Lee}, Runshun Zhang, Baoyan Liu, Xuezhong Zhou, ChengXiang Zhai. \href{https://amia2017.zerista.com/event/member/389402}{Framing Electronic Medical Records as Polylingual Documents in Query Expansion}, \textit{AMIA Annual Symposium Proceedings}. American Medical Informatics Association, 2017.
\item \textbf{[W3]} \textbf{Doris Jung-Lin Lee}, Jinda Han, Dana Chambourova, Ranjitha Kumar. \href{https://kddfashion2017.mybluemix.net/final_submissions/ML4Fashion_paper_21.pdf}{Identifying Fashion Accounts in Social Networks}.  \textit{In Proceedings of ACM KDD 2017 Machine learning meets fashion Workshop}, Halifax, Nova Scotia, August 2017.
\item \textbf{[W2]} Ling Jin, \textbf{Doris Jung-Lin Lee}, Alex Sim, Sam Borgeson, John Wu, Anna Spurlock, Annika Todd, \href{https://aaai.org/ocs/index.php/WS/AAAIW17/paper/view/15166}{Comparison of Clustering Techniques for Residential Energy Behavior using Smart Meter Data}, \textit{2nd International Workshop on Artificial Intelligence for Smart Grids and Smart Buildings} In conjunction with AAAI 2017.
\item \textbf{[W1]} \textbf{Doris Jung-Lin Lee}, Robert J. Brunner, Pattern Discovery and Large-Scale Data Mining on Cosmological Datasets. \textit{6th Workshop on Algorithms for Modern Massive Data Set (MMDS)}, Berkeley, USA, June 2016.
\end{itemize}
\vspace{-10pt}
\section{Technical Reports}
\begin{itemize}[leftmargin=0in,label={}]
\item \textbf{[T2]} \textbf{Doris Jung-Lin Lee}, Aaron T. Lee, astroSim: Jupyter Notebook tutorials for running astrophysical simulations through the gravitational collapse of a magnetized, rotating sphere. [\href{http://doi.org/10.5281/zenodo.59657}{zenodo:59657}]
\item \textbf{[T1]}  \textbf{Doris Jung-Lin Lee}, Robert J. Brunner, Creating updated, scientifically-calibrated mosaic images for the RC3 Catalogue (2015) [\href{http://arxiv.org/abs/1512.01204}{arXiv:1512.01204}]. 
\end{itemize}
\vspace{-10pt}
\section{PRESENTATIONS}
\begin{itemize}
\item Crowdclass: Designing classification-based citizen science learning modules. [\href{http://dorisjunglinlee.com/files/crowdclass_slides.pdf}{Slides}]
	\begin{itemize}[label={$\circ$}]
	\item 10/31/16 HCOMP, Austin, Texas
	\item 10/18/16 UIUC HCI Seminar, Champaign, Illinois
	\item 10/13/16 Zooniverse Seminar at Adler Planetarium, Chicago, Illinois
	\end{itemize}
%\item 06/23/16 \textbf{Doris Jung-Lin Lee}, Robert Brunner, ``Pattern Discovery and Large-Scale Data Mining on Cosmological Datasets".  6th Workshop on Algorithms for Modern Massive Data Set (MMDS).  [\href{http://dorisjunglinlee.com/files/MMDS_poster.pdf}{Poster}]
\item 05/05/16 Alyssa Morrow, Eric Tu, Frank Austin Nothaft, George He, \textbf{Doris Lee},  Anthony Joseph, David Patterson. ``Mango: data exploration on large genomic datasets". UC Berkeley College of Engineering Undergraduate Research Symposium.
\item 08/08/15 \textbf{Doris Lee}, Kengo Tomida, James Stone, ``Three-Dimensional Simulations of Instabilities in Accretion Disk Torus". Princeton University Undergraduate Summer Research Program Final Presentation. [\href{http://dorisjunglinlee.com/files/PrincetonUSRPreport.pdf}{Technical Report}]
\item 03/25/15 \textbf{Doris Lee}, Robert Brunner,``Creating updated, scientifically-calibrated mosaic images for the RC3 Catalogue". Society of Physics Students West Coast Zone Meeting. [\href{http://dorisjunglinlee.com/files/rc3_poster_sps_zone_meeting.pdf}{Poster}]
\end{itemize}
\vspace{-10pt}
\section{PATENTS}
\begin{itemize}
\item \textit{Skintillates: Towards Epidermal Electronics Interactions.} Eric Paulos, Joanne Lo, Jung-Lin Lee, U.S. Provisional Patent Application No.62/174,735, June 2015.
\item \textit{Individually Addressable, Highly Efficient, Trifunctional Conductive Thread.} Eric Paulos, Kimiko Ryokai, Joanne Lo, Laura Devendorf, Jung-Lin Lee, Nan-Wei Gong, Karen Robinson, Ivan Poupyrev, June 2015.
\end{itemize}
\vspace{-10pt}
\section{AWARDS}
\begin{itemize}
\item UIUC Computer Science Excellence Fellowship \rfill Oct 2016
\item ACM DIS 2016 Honorable Mention Award \rfill June 2016
\item ACM CHI 2016 Best Paper Award \rfill May 2016
%\item UC Berkeley Student Opportunity Fund Travel Award \hspace{15pt}\tab{March 2016}
\end{itemize}
\vspace{-10pt}
\section{SERVICE} 
\itab{} \itab{Students Mentored:}
\begin{denselist}
    \item Jaewoo Kim  \studentinfo{Undergraduate Senior Thesis; Now Graduate Student at UIUC} \rfill 2017-Present
    \item Huizi Hu \studentinfo{BS CS '19} \rfill 2017-Present
    \item Renxuan Wang  \studentinfo{MS CS'19} \rfill 2018-Present
    \item Jintao Jiang  \studentinfo{BS CS '18} \rfill 2018-Present
    \item Edward Xue   \studentinfo{MS CS '18; Now software engineer at Facebook} \rfill 2017-18
    \item Marc Lee \studentinfo{MS Stats '18}\rfill 2018
    \item Xu Yang \studentinfo{MS IE '18}\rfill 2018
    \item Chaoran Wang \studentinfo{MS CS '17; Now software engineer at Uber} \rfill 2017
    \item Zhiwei Zhang \studentinfo{BS CS '17; Now software engineer at DRW} \rfill 2017
    \item Yanqing Ma \studentinfo{BS CS '19} \rfill 2017
    \item Dana Chambourova \studentinfo{Undergraduate Senior Thesis; Now software engineer at Flexport}\rfill 2017
    \item Moonhyook Kim \studentinfo{BS CS '16} \rfill 2016
\end{denselist}
\itab{} \itab{ACM IUI Paper Program Committee} \rfill 2018, 2019  
\\ \itab{} \itab{Paper Reviewer: ACM CHI 2019 (Case Studies), TIIS 2018, CHI 2018, IUI 2017, IUI 2019 (Poster Demo), EuroVis 2019}\hspace{279pt}
\\ \itab{} \itab{Mentoring \& Volunteering Programs:}
\begin{denselist} 
    \item UIUC CS Department Graduate Student Mentor (2018)
    \item UIUC CS Department Graduate Student Ambassador (2018)
    \item UIUC Mentoring Undergraduates in Science \& Engineering (2017)
    \item Peer Mentor and Club Liaison for UC Berkeley Society of Physics Students (2015-2016)
    \item Volunteer and Summer Program Coordinator at UC Berkeley COMPASS Project (2013-2016)
\end{denselist}
% \\ \itab{} \itab{ACM TIIS 2018 Reviewer}\hspace{279pt}
% \\ \itab{} \itab{ACM CHI 2018 Reviewer}\hspace{279pt}
\itab{} \itab{ACM SIGCHI Executive Committee Student Volunteer} \rfill 2017
% \\ \itab{} \itab{ACM IUI 2017 Reviewer}\hspace{279pt}
\\ \itab{} \itab{ACM XRDS Magazine News Editor}\rfill Nov 2014-August 2016
% \\ \itab{} \itab{Organization Mentor for Google Code-In youth programming contest}\hspace{279pt}\tab{2015-2016 Season}

% \\ \itab{} \itab{Peer Mentor and Club Liaison for Society of Physics Students}\hspace{266pt}\tab{Sept 2015-May 2016}
% \\ \itab{} \itabf{Volunteer and Summer Program Coordinator at Berkeley COMPASS Project}\hspace{267pt}\tab{Sept 2013-May 2016}
\end{resume}
\end{document}