\documentclass{res} 
\usepackage{enumitem}
\usepackage{hyperref}
\hypersetup{colorlinks,urlcolor=black}
\newsectionwidth{10pt}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newcommand{\tab}[1]{\hspace{.2\textwidth}\rlap{#1}}
%\documentcliass[11pt]{article} %Sets the default text size to 11pt and class to article.
%------------------------
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 
\linespread{1.15} %This controls line spacing throughout the whole document 
\begin{document}
\raggedright
\centerline{\LARGE \textbf{Doris Jung-Lin Lee}} 
\vspace{-10pt}
\noindent %Prevents the following text from being indented
\centerline{ \href{mailto:dorisjunglinlee@gmail.com}{dorisjunglinlee@gmail.com} $\bullet$
\href{http://dorisjunglinlee.com}{dorisjunglinlee.com}$\bullet$
 GitHub: \href{https://github.com/dorisjlee}{dorisjlee} }
\vspace{1pt}
\\ \centerline{(510)-731-8742 $\bullet$ Apt \#308, 201 S. Wright Street, Champaign, IL, 61820} 
 \vspace{5pt}
\begin{resume}
\vspace{-30pt}
\section{EDUCATION}
\vspace{5pt}  
    \itab{Ph.D. Compute Science, University of Illinois, Urbana-Champaign} \tab{} \tab{} \tab{\quad\quad\quad\quad\quad\quad\quad\quad\quad Aug 2016 - Present} \\
\vspace{5pt}  
    \itab{B.A. Physics, Astrophysics, University of California, Berkeley} \tab{} \tab{} \tab{\quad\quad\quad\quad\quad\quad\quad\quad Sept 2013 - May 2016}
\vspace{-10pt}
\section{RESEARCH EXPERIENCE}
\vspace{-10pt}
     \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill 
   \vspace{-20pt}
    {\bf Graduate Student Research Assistant at UIUC}  \>\hspace{205pt}  Aug 2016 - Present
        \\ %UIUC Data-Driven Design Group
   \end{tabbing}    
    \begin{itemize}
     \vspace{-20pt}
     %Developing machine learning models for analyzing data streams from social \\media  and new product reviews in fashion. 
     \item  Applying machine learning techniques to problems in human-computer interaction and design. Analyzing data streams from social media  and new product reviews in fashion. 
     \item Modelling work quality evaluation for crowdsourcing image segmentation.
     \item Developing user-expectation models for finding interesting data visualizations.
     \end{itemize}
\vspace{-20pt}     
     \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill 
   \vspace{-20pt}
    {\bf Lawrence Berkeley National Lab Scientific Data Management Group}  \>\hspace{195pt}  May 2016 - Aug 2016
        \\ 
   \end{tabbing}    
    \begin{itemize}
     \vspace{-20pt}
     \item  Comparison of load profile clustering techniques and behavioural analytics \\predictions for residential electricity usage. 
     \end{itemize}
     \vspace{-20pt}   
     \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill 
   \vspace{-20pt}
    {\bf Berkeley AMP Lab}  \>\hspace{180 pt}  January 2016 - Aug 2016
        \\ 
   \end{tabbing}    
    \begin{itemize}
     \vspace{-20pt}
     \item  Developing data visualization for Mango, a scalable genome browser for \\analyzing reads, variants, and features built on top of the ADAM genomics \\processing engine and Spark.  Paper in prep. for \textit{Nucleic Acids Research}.
     \end{itemize}
     \vspace{-20pt}   
     \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill 
    {\bf Berkeley Star Formation Simulation Research}  \>\hspace{171pt}  November 2014 - Aug 2016
        \\ 
   \end{tabbing}    
    \begin{itemize}
     \vspace{-20pt}
%     University of California Berkeley  Department of Astronomy
     \item  Investigating the effect of magnetic fields in protostar formation. Designing\\ parallel, adaptive mesh refinement, magnetohydrodynamical simulations \\ on supercomputers to track the evolution of a collapsing dense core.
     \end{itemize}
     \vspace{-20pt}
        \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill 
    {\bf  Berkeley Human-Computer Interaction Group} \>\hspace{193pt}  June 2014 - Aug 2016
        \\ 
   \end{tabbing}  
   \vspace{-20pt}
     \begin{itemize}
	\item Designing new educational software approaches to conventional mechanical turk \\ classification tasks in citizen science. 
     \item Collaborated with Google ATAP in Project Jacquard, a new e-textile technology.  
     \item Creating low-cost fabrication technique for on-skin wearable electronics.  Developed \\a ferro-fluid sketching technique as a new interactive interface. Refined a fabrication \\pipeline for rapid prototyping PCB-like circuits using flexible polystyrene plastic \\sheets as substrates.
     \end{itemize}
     \vspace{-15pt}
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill 
    {\bf  University of Illinois Laboratory for Cosmological Data Mining}  \> \>\hspace{7pt} May 2014 - Jan 2016
   \\
   \end{tabbing}\vspace{-20pt}    
     \begin{itemize}
     \item Applying unsupervised machine learning algorithms to search for dark matter \\haloes in  large-scale N-body cosmological simulations.
     \item  Developed an adaptive algorithm that performs positional update on catalog \\sources for constructing a newer version of the RC3-cataloged galaxies. Designed \\a general software pipeline for creating scientifically-calibrated mosaics from \\large survey imaging datasets and an online database for accessing data products.  
     \end{itemize}
       \vspace{-15pt}
\begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill 
   \vspace{-30pt}
    {\bf Princeton Astrophysical Fluid Dynamics Group}  \>\> \hspace{34pt} Summer 2015 
    \\ 
   \end{tabbing}    
    \begin{itemize}
     \vspace{-20pt}
     \item Constructed global, magnetohydrodynamical disk simulations on supercomputers for \\testing the new \textit{Athena++} code. Explored the effects of Papaloizou-Pringle and \\magnetorotational instabilities on accretion disk torus. 
     \end{itemize}    \vspace{-10pt}   
\section{PUBLICATIONS}
\begin{itemize}
%\item Alyssa Morrow, Eric Tu, Frank Austin Nothaft, \textbf{Doris Jung-Lin Lee}, George He, Anthony D. Joseph, David A. Patterson. Mango: data exploration on large genomic datasets. In preparation for \textit{Nucleic Acids Research}.
\item Ling Jin, \textbf{Doris Lee}, Alex Sim, Sam Borgeson, John Wu, Anna Spurlock and Annika Todd, \href{https://sdm.lbl.gov/perf/AISGSB2017-final2.pdf}{Comparison of Clustering Techniques for Residential Energy Behavior using Smart Meter Data}, \textit{2nd International Workshop on Artificial Intelligence for Smart Grids and Smart Buildings} In conjunction with AAAI 2017.
\item \href{http://aaai.org/ocs/index.php/HCOMP/HCOMP16/paper/viewFile/14027/13638}{\textbf{Doris Jung-Lin Lee}, Joanne Lo, Moonhyok Kim, Eric Paulos, Crowdclass: Designing classification-based citizen science learning modules. \textit{The Fourth AAAI Conference on Human Computation and Crowdsourcing (HCOMP 2016)}, Austin, Texas, November 2016.}
\item \href{http://dl.acm.org/citation.cfm?id=2901885&CFID=765226474&CFTOKEN=46922780}{Joanne Lo, \textbf{Doris Jung-Lin Lee}, Nathan Wong, David Bui, Eric Paulos,``Skintillates: Towards Epidermal Interactions".  \textit{ACM Designing Interactive Systems (DIS)}, Brisbane, Australia, June 2016. \textit{Honorable Mention.}}
\item \href{http://dl.acm.org/citation.cfm?id=2858192&CFID=765226474&CFTOKEN=46922780}{Laura Devendorf, Joanne Lo, Noura Howell, \textbf{Jung Lin Lee}, Nan-Wei Gong, M. Emre Karagozler, Ivan  Poupyrev, Eric Paulos, Kimiko Ryokai,``\hspace{1pt}`I don’t want to wear a screen': Probing perceptions of and  possibilities for dynamic displays on clothing''. \textit{ACM Transactions on Computer-Human Interaction (CHI)}, San Jose, USA, May 2016. \textit{Best Paper Award.}}
\item \textbf{Jung Lin Lee}, Robert J. Brunner, ``Creating updated, scientifically-calibrated mosaic images for the RC3 Catalogue"(2015) [\href{http://arxiv.org/abs/1512.01204}{arXiv:1512.01204}]. 
\end{itemize}
\section{PRESENTATIONS}
\begin{itemize}
\item Crowdclass: Designing classification-based citizen science learning modules. [\href{http://dorisjunglinlee.com/files/crowdclass_slides.pdf}{Slides}]
	\begin{itemize}[label={$\circ$}]
	\item 10/31/16 HCOMP, Austin, Texas
	\item 10/18/16 UIUC HCI Seminar, Champaign, Illinois
	\item 10/13/16 Zooniverse Seminar, Chicago, Illinois
	\end{itemize}
\item 06/23/16 \textbf{Doris Jung-Lin Lee}, Robert Brunner, ``Pattern Discovery and Large-Scale Data Mining on Cosmological Datasets".  6th Workshop on Algorithms for Modern Massive Data Set (MMDS).  [\href{http://dorisjunglinlee.com/files/MMDS_poster.pdf}{Poster}]
\item 08/08/15 \textbf{Jung Lin Lee}, Kengo Tomida, James Stone, ``Three-Dimensional Simulations of Instabilities in Accretion Disk Torus". Princeton University Undergraduate Summer Research Program Final Presentation. August 2015. \href{http ://dorisjunglinlee.com/files/PrincetonUSRPreport.pdf}[{Technical Report}]
\item 03/25/15 \textbf{Jung Lin Lee}, Robert Brunner, ``Creating updated, scientifically-calibrated mosaic images for the RC3 Catalogue". Society of Physics Students West Coast Zone Meeting. March 2015. [\href{http://dorisjunglinlee.com/files/rc3_poster_sps_zone_meeting.pdf}{Poster}]
\end{itemize}
\section{PATENTS}
\begin{itemize}
\item \textit{Skintillates: Towards Epidermal Electronics Interactions.} Eric Paulos, Joanne Lo, \textbf{Jung-Lin Lee}, U.S. Provisional Patent Application No.62/174,735, June 2015.
\item \textit{Individually Addressable, Highly Efficient, Trifunctional Conductive Thread.} Eric Paulos, Kimiko Ryokai, Joanne Lo, Laura Devendorf, \textbf{Jung-Lin Lee}, Nan-wei Gong, Karen Robinson, Ivan Poupyrev, June 2015.
\end{itemize}
\section{AWARDS}
\begin{itemize}
\item Computer Science Excellence Fellowship \hspace{108pt}\tab{Oct 2016}
\item ACM DIS 2016 Honorable Mention Award \hspace{95pt}\tab{June 2016}
\item ACM CHI 2016 Best Paper Award\hspace{133pt}\tab{May 2016}
%\item UC Berkeley Student Opportunity Fund Travel Award \hspace{15pt}\tab{March 2016}
\end{itemize}
%\section{SERVICE} 
%\itab{} \itab{Reviewer IUI 2017}\hspace{279pt}
%\\ \itab{} \itab{News Editor for Association for Computing Machinery Student Magazine}\hspace{279pt}\tab{Nov 2014-August 2016}
%\section{ACTIVITIES}        
%\itab{} \itab{Organization Mentor for Google Code-in youth programming contest}\hspace{279pt}\tab{2015-2016 Season}

%\\ \itab{} \itab{Club Liaison for Society of Physics Students}\hspace{277pt}\tab{Sept 2014-May 2016}
%\\ \itab{} \itab{Peer Mentor for Society of Physics Students}\hspace{277pt}\tab{Sept 2015-May 2016}		
%\\ \itab{}\itab{ Volunteer and Summer Program Coordinator at Berkeley COMPASS Project}\hspace{280pt}\tab{Sept 2013-May 2016}
\end{resume}
\end{document}